Signal Processing to Demodulate FM Radio

### 2020-12-16 doc/paper/paper.tex
notes
start FM demod

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FM Signal Demodulation}
\label{sec_fm_sig_demod}
    % mono:   just LP on 15 kHz
    % stereo: sum (L+R) + (L-R) = 2 L, (L+R) - (L-R) = 2R
  \subsection{Baseband Delay Demodulator}
  \subsection{Phase-Adapter Demodulator}
  \subsection{Phase-Locked Loop (PLL)}
  \subsection{Mixed Demodulator}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FM Signal Demodulation}
\label{sec_fm_sig_demod}
  An FM signal that is received by an antenna needs to be demodulated, in order to decode its actual data content.
  The radio-frequency antenna signal usually needs to be amplified, bandpass-filtered, and down-converted to baseband, using subsampling and quadrature-mixing, or similar strategies.
  This part of the signal processing chain is assumed to be working correctly and is out of the scope of this paper.
  The FM signal that is evaluated here, is assumed to be a quadrature-mixed signal in baseband, which means that inphase and quadrature (I/Q-) signals are available.
  %TODO: show downconversion path (maybe as a figure?)
  %https://www.veron.nl/wp-content/uploads/2014/01/FmDemodulator.pdf

  % mono:   just LP on 15 kHz
  % stereo: sum (L+R) + (L-R) = 2 L, (L+R) - (L-R) = 2R
  % page 30: https://www.hs-schmalkalden.de/fileadmin/portal/Dokumente/Fakult%C3%A4t_ET/Personal/Roppel/Buch/Analoge_Modulationsverfahren.pdf

  \subsection{FM-AM-Demodulator}
    convert FM to AM
    %https://www.tutorialspoint.com/analog_communication/analog_communication_fm_demodulators.htm
    %sect 3.3 : https://www.hs-schmalkalden.de/fileadmin/portal/Dokumente/Fakult%C3%A4t_ET/Personal/Roppel/Buch/Analoge_Modulationsverfahren.pdf

  \subsection{Phase-Locked Loop (PLL)}
